Against the Planetary Interpretation of PTFO$\,$8-8695b

### 2020-04-02 paper/ms.tex
update paper

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f4.png}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf foo.}
		bar
		\label{fig:o_minus_c}
	}
\end{figure*}

@@

\paragraph{Fourier analysis}
Figure~\ref{fig:splitsignal} could also be given in the frequency
domain, rather than the time domain.
The largest peaks in 
the Lomb-Scargle periodogram (CITE) of the raw light-curve are
at $P_\rm {s}$ and $P_{\rm \ell}$.
Both peaks of course have aliases.
The $P_\rm {\ell}$ peak has larger ampitude.
Subtracting out the long-period signal, the short-period signal
dominates the periodogram, and vice-versa.
The periodogram of the final residual (Figure~\ref{fig:splitsignal}
bottom row) shows a weakly significant, poorly resolved peak at
$\approx$8 days, consistent with the visual impression in the time
domain that there could be a weak long-period signal present.

>>>>

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Timing residuals for PTFO 8-8695b from a decade of monitoring.}
		Black points are times of ``dips'', minus the indicated linear ephemeris.
    The $y$-axis is given in units of phase for the
    short-period signal.
    The star shows the binned TESS ephemeris.
		``Dips'' have been observed by
		\citet{van_eyken_ptf_2012}, \citet{ciardi_follow-up_2015},
		\citet{yu_tests_2015}, \citet{raetz_yeti_2016},
		\citet{onitsuka_multi-color_2017}, and \citet{tanimoto_evidence_2020}.
    Certain dips ({\it e.g.}, the one at phase 0 in mid-2019) are
    consistent with noise, and were likely reported because
    something was {\it expected}, rather than convincingly {\it
    observed}.
    Horizontal dashed lines are drawn at $\pm (P_{\rm \ell} - P_{\rm s})/P_{\rm s}$,
    highlighting what could be either a numerical coincidence or an observational
    bias.
    The orbital phase observed by TESS is consistent with that of \citet{tanimoto_evidence_2020}, and quite different from the original phase.
		\label{fig:o_minus_c}
	}
\end{figure*}

@@

\paragraph{Fourier analysis}
Figure~\ref{fig:splitsignal} could also be given in the frequency
domain, rather than the time domain.
The largest peaks in 
the Lomb-Scargle periodogram (CITE) of the raw light-curve are
at $P_{\rm s}$ and $P_{\rm \ell}$.
Both peaks of course have aliases.
The $P_{\rm \ell}$ peak has larger ampitude.
Subtracting out the long-period signal, the short-period signal
dominates the periodogram, and vice-versa.
The periodogram of the final residual (Figure~\ref{fig:splitsignal}
bottom row) shows a weakly significant, poorly resolved peak at
$\approx$8 days, consistent with the visual impression in the time
domain that there could be a weak long-period signal present.
